Elements of meaningful data sharing

### 2020-12-01 new-paper.Rmd
minor changes from meeting today with Karthik

---
title: Meaningful data sharing
author: Nicholas J Tierney\* (1,2) & Karthik Ram\* (3)
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
csl: nature-communications.csl
header-includes: 
  - \setstretch{1.45}
  - \usepackage[utf8]{inputenc}
---

@@

- Data sharing practices to realign incentives and enable positive/meaningful culture change\\
- Enabling culture change for meaningful data sharing\\
- Enabling culture change for meaningful data sharing: Aligning incentives and minimally acceptable practices\\
- Principles of sharing data\\
- Elements of meaningful data sharing\\
- Minimally acceptable practices in data sharing to enable culture change\\

@@

>>>>

---
title: Elements of meaningful data sharing
author: Nicholas J Tierney\* (1,2) & Karthik Ram\* (3)
output:
  bookdown::pdf_document2:
    keep_tex: true
    toc: no
    includes:
      in_header: preamble.tex
bibliography: references.bib
csl: nature-communications.csl
header-includes: 
  - \setstretch{1.45}
  - \usepackage[utf8]{inputenc}
---

@@

- Meaningful data sharing
- Data sharing practices to realign incentives and enable positive/meaningful culture change\\
- Enabling culture change for meaningful data sharing\\
- Enabling culture change for meaningful data sharing: Aligning incentives and minimally acceptable practices\\
- Principles of sharing data\\
- Elements of meaningful data sharing\\
- Minimally acceptable practices in data sharing to enable culture change\\

@@

We limit the scope of this paper to small to medium sized tabular data as it covers a vast majority of use cases that researchers encounter day to day. For larger datasets that involve complex workflows (e.g., bioinformatics and medical imaging), the kinds of challenges they face are different and accordingly deserve to be written up separately.
